The main goal is to install a toothbrush production line in the eco-city of Taijin in China.
Our company is workig for \moldco to make this production line a reality.

Our main guideline in this project is to install a production line that can produce a great amount of toothbrushes within an eco-city.
This project needs to be respectful of the surrounding environnement and social aspects of the project's stakeholders.

\subsection{Specifications}

This project has to achieve the following specifications.

The production line must contains all the required machines to automate the production of toothbrushes.
Theses machines include moulting machine, stamping machine, tufting machine, bristle cutter machine, bristle trimming machine and Packaging machine.
These machines need to be bought and connected to each other in order to build the full product.

To connect all the machines in the assembly line, the project requires also a full digital connection to an internal network.
This network group all connected machines and database servers to store monitoring informations about the production.
These informations represents the current production, the past production and potential errors in the production line.

The production line is fully automated through this network and the production is regulated to produce exactly what is needed.
This automatisation brings many advantages including the environmental impact reduction, reduction of the storage requirement of finished products and 24/7 production in case of huge demand.

The informations collected need to be displayed to the employees in charge of the production line.
These informations are displayed through an interface reading the monitoring data from the database.
A master server has to be installed in order to control all machines and to control the production flow.

Several materials are required to produce toothbrushes.
These materials are plastics, nylons, brass wires, papers box packing, plastinc hard container packaging, high frequency blister packaging and blister card packaging.
The project must include a storage space for all these material and human resources to load the resources in the appropriate machines.

All the production line machines, storage and digital network requires engineering the organise all these components depending on the space available and the shape of the building.
Enginieering human resources are required to create, configure and install manitoring system.
Human resources may also be required to manipulate machines, connect each machine to the other and install network.

\subsection{Strenghts}

The strenghts of the project are mainly focused on the high effeciency of the production line.
This high effeciency is garanteed by the monitoring system and the automatic management of the amount of product produced on the assembly line.
This project represents a great opportunity to modernize the production of \moldco and automate the assembly line.
By automating the assembly line, \moldco gain a lot of money on storage of manufatured products and human resources.

\subsection{Weaknesses}

This project have also small weakness that may have an impact on risks
(Risk managment will be covered in the section \ref{risk-management}).

The main weakness are the important amount of advanced technologies that requires high qualified employees in charge of the installing and maintaining the autonomous system of the assembly line.
Another weakness is the requirement of heavy and pricy machines that can represent a major part of the project's costs.

\subsection{Social \& Environmental guidelines}

As our project takes place in the eco-city of Tianjin, it must include proper social and environmental guidelines.
Theses guidelines are and must be evaluated during the project to qualify if these are possible to set up with \moldco budget.

\subsubsection{Social engagement for project human resources}

These guidelines includes social engagements for the well being of employees and human resources during the project.

\paragraph{Working hours} For employeese better productivity, it could be good to restrict to 8 hours the day of work to complete a full week withing 44 hours.
We must audit reguarly our employees about their opinion and well-being within the company through feedbacks.

\paragraph{Human rights and equity} Our project must respect the human rights about children labor or unpaid employees.
These are forbidden.
Finally, our employees salary musn't depend on gender, race or physical ability. 

\paragraph{Health} Thus, our project is about health product.
We must establish health requiremets to reduce bacterial or viruses risks during toothbrushes production.
We must include protection against noise and injury risks on the production line.
That include collective equipments like protective foam, barrier, etc.
But also personnal equipement like hear protections, gloves, etc.
And we could give an introduction to the handling of machines for all employees to avoid injuries.

\subsubsection{Environmental guidelines}

\paragraph{Waste and recycling} We must establish a plan and write good practicies about material waste in order to reduce our waste that have a huge environmental impact.
Our automation system must optimise production in order to reduce waste.
We could also collect rainwater in order to use it in bathrooms or for floor washing.

\paragraph{Effeciency} We could invest in machines that are more profitable and resource-efficient to reduce the resources required to get the assembly line working.
Moreover, it could be good to progressively invest in renewable energy in order to reduce our energy-related environmental impact.
This includes solar panels, wind turbines or heat pumps that can be installed outside of the building or on employees parking.

\paragraph{Building optimizations} The whole building could include some automations to reduce environmental impact and reduce energy waste.
These automations includes auto-switch lights and computers when there are not used.

\paragraph{Machine repairs} To reduce environmental impact and keep our machines as long as possible, it's possible to introduce a repair culture during the project and after.
This repair guidelines include bying repairable machines, recycle spare parts of deffective machines and train employees about machine repairing.

\paragraph{Delivery guidelines} Delivery is a huge part of our environmental impact.
To reduce it, we could group most of our delivery to reduce waste of space in polluting transports like trucks.
We could also promote rail transport over trucks transport. This transport method are way less polluting but more expensive. However high-speed train are actually developing in china, thus it would be less expansivein the future.

\subsection{Local investments \& suppliers}

\paragraph{Local investment} It could be good, to participate in local project of Taijin.
This investments could represent a good opportunity to communicate on the green engagement of \moldco.

\paragraph{suppliers guidelines} \moldco must audit it's suppliers in order to evaluate there social and environmental impact and be sure they fits with our own requirements.

\paragraph{Local implication} Our factory is in a city and \moldco must communicate with local authorities about what it's happening in the factory.
Local authorities include Tanjin City Hall and People's Republic of China government.
\moldco must inform authorities about environmental risks and how we will manage it in such case.
We also require to be informed about local chinese health and sanitary requiremet in order to be consistent with it.